HSC Synthetic Pipeline I: Basic Design and Characterization of HSC Photometric Performance

### 2017-04-19 draft/ms_susan.tex
New edits from Susan

    %% Challenges
    Before we can tackle any outstanding scientific questions, we must first learn
    how to handle the huge amount of data\footnote{Right now, SSP has accumulated 
    ${\sim}300$ TB of data products.} generated by these projects as well as achieve
    accurate photometric measurements of different types of objects.
    Data handling becomes increasingly challenging in the age of modern imaging
    surveys, in part due to variations and effects related to the cameras' 
    charge-coupled devices (CCDs).
    The cameras are often made up of multiple CCDs, each with slightly different 
    characteristics, and have large fields-of-view (FoV) over not perfectly flat 
    focus planes.
    During observation, the seeing and background conditions always show spatial
    and temporal variations across the FoV.
    The full-depletion, thick CCDs selected for the cameras enable long exposure 
    times and excellent sensitivity in the red-end, but they often suffer from the 
    so-called ``brighter-fatter'' effect (\citealt{Antilogus2014}), which means that 
    brighter stars appear larger than they are.
    These variations and effects make accurate astrometric and photometric calibration,
    background subtraction, and point spread function (PSF) modeling intrinsically
    difficult (e.g., \citealt{Schlafly2012}).
    The multi-epoch, multi-band nature of the surveys also complicate data reduction 
    because the scientist must pay special attention to image stacking, multi-band 
    object detection, and measurement processes.
    Furthermore, as ongoing surveys reach to increasingly deeper detection limit 
    (e.g SSP Wide reaches to $5\ \sigma$ detection limit of point source of 
    ${\sim}26.4$ mag), the number of objects in a unit area, especially faint objects,
    becomes much higher. 
    In addition, it is much more common to observe objects that overlap each other at
    different levels (a phenomenon often referred to as ``blended'').
    These modern imaging survey challenges call for photometric measurement methods 
    that are more powerful and precise than those used in previous, shallower surveys.

@@

%% ------------------------------------------------------------------------------------ %%
%% Fig: Flowchart
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_flowchart_new}
    \end{center}
    \caption{
        Illustration of \synpipe{} basic procedures.
        Grey boxes indicate the required inputs at different stages.
        The blue box identifies the \texttt{addFakes.py} step, when \synpipe{} injects 
        simulated images of synthetic objects onto a single-frame image. 
        We show an example CCD image with and without synthetic objects on it
        (highlighted by green circles).
        Red boxes depict the subsequent image coadding and multiband measurement steps
        using \texttt{stack.py} and \texttt{multiBand.py} from \hscpipe{}.
        We show a small piece of \coadd{} image with synthetic objects on it.
        The figure on the right side of the middle row shows the spatial relation
        between \tract{} (outlined by the black dashed lines; each small region
        is a \texttt{Patch}) and all the \visits{} that contribute to it. 
        (Each \visit{} has a  unique color; each small region is the size of a CCD.)
        }
    \label{fig:flowchart}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    %% Basic
    Taking advantage of the new prime focus camera on the 8.2--m Subaru telescope,
    the ambitious HSC survey consists of three layers: Wide, Deep, and UltraDeep.
    The Wide layer will map a total of ${\sim}1400$ deg$^2$ of sky in five broad bands
    ($grizy$; Kawanomoto\etal in prep.).
    The Deep (4 separated fields; ${\sim}27$ deg$^2$) and UltraDeep (2 separated
    fields; ${\sim}3.5$ deg$^2$) layers will use a few additional narrow-band filters
    and employ a slightly different surveying strategy.
    Strauss\etal (in prep.) describes the HSC survey in more detail, and identifies the 
    HSC collaborators.

    The HSC camera (\citealt{Miyazaki2012}) is made up of 124 full-depletion thick 
    CCDs: 112 for science and another 12 for guiding and focusing.
    The camera has a circular FoV with a 1.5 deg diameter.
    Each CCD contains 2048$\times$4096 pixels distributed in 4 amplifiers.
    The pixel size is equal to 0.168\asec{} on the sky.

    In February 2017, the HSC collaboration released the first 1.7 years of data to 
    the public (DR1; 
    \citealt{HSCDR1})\footnote{\texttt{https://hsc-release.mtk.nao.ac.jp }}.
    For our work, we focused on data from the Wide layer as they relate to key 
    scientific goals of HSC survey, which include WL cosmology, galaxy evolution 
    since $z{\sim}1$, and studies of galaxy clusters.
    The current Wide layer includes ${\sim}108$ deg$^2$ of sky isolated in
    6 different regions (XMM--LSS, GAMA09H, WIDE12H, GAMA15H, HECTOMAP, and VVDS)
    \footnote{A small AEGIS field is also observed for calibration purposes.}.
    Except for the HECTOMAP field, the regions are all close to the equator. 
    In the Wide layer, the $g$ and $r$ bands have 10 mins of exposure broken into 4
    dithers\footnote{Large, ${\sim}1/3$ of the FoV dither pattern is used to ensure
    uniform coverage.}; for the remaining 3 bands, 20 mins of exposure time and 6 
    dithers are used\footnote{Several 30 s exposures are taken to improve the 
    dynamic range.}.
    The survey prioritizes the observations so that the $i$-band can have excellent
    seeing conditions to help make accurate WL shape measurements.
    The current Wide layer has impressive median seeing with FWHM${\sim}0.6$\asec{},
    and has a $i{\sim} 26.4$ mag $5\sigma$ point source detection limit. 
    \citealt{HSCDR1} provides details on the first data release and data status.

@@

        \item \textbf{HSC Photometry}:
            The multi-band catalogs generated by \hscpipe{} contain a variety of 
            photometric information (see \citealt{HSCDR1} for details).
            \textbf{Here, we focus on the \forced{} \texttt{psf} and \cmodel{}
            photometry.}
            \texttt{psf} photometry should provide the most appropriate magnitudes and
            colors for point sources.
            Improved over the SDSS version (\citealt{Lupton2001, Abazajian2004}),
            the HSC \cmodel{} algorithm (described in Bosch\etal, in prep.) fits 
            each object's flux distribution using a combination of the de Vaucouleur
            profile and an exponential component that takes the PSF convolution 
            into account.
            \cmodel{} is designed to yield accurate colors for galaxies.
            In addition, the star--galaxy classification task is performed based on 
            the difference between the \texttt{psf} and \cmodel{}{} magnitudes.

@@

        \item \textbf{Authentic Data Processing}:
            To follow the data reduction process as realistic as possible, we choose to
            start from the single-\visit{} images instead of directly putting synthetic 
            objects on the final \coadd{} images (e.g., \citealt{Suchyta2016}).
            Through this approach, subtle effects like seeing differences among
            \visits{} and small errors in astrometric calibration can be taken
            into account.
            Every synthetic object will experience all the steps we would use for any 
            real object: detection, deblending, stacking, and measurement.
            This can be important for challenging tasks like the WL measurements
            or the detection of high-$z$ galaxies.
            The only downside of this choice is that it will certainly slow down the
            test for \coadd{} images because in this approach we need to inject 
            synthetic objects into all the \visits{} that contribute to a \tract{}.

@@

        \item \textbf{Single- or Double-\ser{} model for galaxy}:
            \texttt{SynPipe} uses \galsim{} \texttt{v1.4} (\citealt{Rowe2015}) to
            simulate a galaxy.
            \galsim{} is an image simulation tool that has been well tested during
            the GRavitational lEnsing Accuracy Testing 3 (GREAT3) challenge 
            (\citealt{Mandelbaum2014}).
            Currently, \synpipe{} allows a synthetic galaxy to be modeled by single
            or double components that are described by the \citet{Sersic1963}
            profile\footnote{More flexible model choices will be added later.}.
            The \ser{} profile is flexible enough to describe the overall flux
            distributions of galaxies near and far, both early-type or late-type.
            A Double-\ser{} model can simulate a galaxy with even more realistic
            structural details (e.g., bulge$+$disk).
            For each \ser{} component, the user needs to provide the magnitude,
            effective radius ($R_{\mathrm{e}}$; in unit of arcsec), \ser{} index
            ($n_{\mathrm{Ser}}$), axis ratio ($\mathrm{b}/\mathrm{a}$), and position
            angle (PA).
            External shear can also be applied to a synthetic galaxy ($g_1$ and 
            $g_2$; see \citealt{Rowe2015} for more details).

@@

    After \synpipe{} creates the image of the simulated galaxy, it then shifts the 
    image according to is location on the CCD on a pixel-by-pixel basis; 
    \synpipe{} also crops the images when necessary.
    When that task is complete, \synpipe{} adds appropriate noise to the image based 
    on the pixels it covers and the calibration information of the detector, and creates 
    a variance image that reflects the influence of the synthetic object.
    Since each HSC CCD consists of four amplifiers, each with different characteristics,
    \synpipe{} carefully creates a corresponding gain map to provide accurate noise 
    level.
    In the final step, \synpipe{} adds the noise-added image and the variance map to the
    original CCD data while also adding a new \texttt{FAKE} mask bit to the mask plane.
    The middle panel of Fig \ref{fig:flowchart} depicts the result of the
    \texttt{addFakes.py} step by showing an example CCD image before and after the
    synthetic objects are injected.
%% ------------------------------------------------------------------------------------ %%

@@

    As the last step, \synpipe{} matches the input catalog to the results within a
    radius that is specified by the user, and merge all the \unforced{} and
    \forced{} measurements from all the \texttt{Patches}.
    Each unmatched object from the input catalog is also passed to the results catalog 
    with a unique label.
    In case of multiple matches, the user can choose between returning only the 
    closest match or returning all objects within the matching radius (the nearest one 
    is labeled as such).

    \song{Susan's edit ends here; and Song has went through the previous sections.}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %%
%% Fig: Star Sample
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_star_sample}
    \end{center}
    \caption{
        Magnitude and color distributions of the synthetic stars.
        \textbf{Upper panel} shows the 5-band magnitude distributions of the COSMOS
        stars (filled histograms) and the resampled stars (dashed lines).
        \textbf{Lower panel} shows their color-color distributions
        (left: $g-r$ v.s. $r-i$; right: $i-z$ v.s. $z-y$).
        We show the number density distribution of the COSMOS stars in hexagonal bins,
        and use contours for the resampled stars.
        }
    \label{fig:star_sample}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %%
%% Fig: Galaxy Sample
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_galaxy_sample}
    \end{center}
    \caption{
        Distributions of 5-band magnitudes (\textbf{upper panel}) and other properties
        (\texttt{lower panel}; from left to right are the \ser{} index, axis ratio,
        effective radius in arcsec, the $g-r$ and $r-z$ colors) of the synthetic
        galaxies.
        Objects used for the \textbf{Tract} with good seeing (filled histograms) and
        the one with bad seeing (dashed line) have almost identical distributions.
        }
    \label{fig:galaxy_sample}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %%
\section{Generation of Synthetic Dataset}
    \label{sec:test}

@@

    Given the design of \synpipe{} and the data volume of HSC DR1\footnote{${\sim}70$
    TB of images}, it is not realistic to test the whole dataset.
    For this work, we select two \tracts{} in HSC Wide regions
    that fit the following criteria:

@@

        \item Not bothered by extremely bright ($i<12$ mag), saturated star.

        \item Can represent good and bad seeing condition in the current $i$-band
            data of HSC survey.
            For the same star or galaxy, different seeing conditions affect its
            central S/N on the \coadd{} images, hence it also impacts the
            detection and deblending processes in \hscpipe{}.
            Therefore, it is useful to show the photometric uncertainties under
            different seeing conditions.

    \noindent These regions are:
    \tract{}$=9699$ in the VVDS field (median FWHM$=0.449$\asec{} in $i$-band;
    will be referred as \texttt{goodSeeing}) and
    \tract{}$=8764$ in the XMM-LSS field (median FWHM$=0.700$\asec{};
    \texttt{badSeeing}).
    \tract{}$=9699$ also has better seeing in both $r$ and $z$-band;
    their seeing conditions in $g$ and $y$ bands are very similar.
    For both \tracts{}, the \coadd{} image in each band includes data from
    20--40 \visits{}.

@@

    In this work, we use objects from the high-resolution \hst{}/ACS observations of
    the COSMOS field to build input catalogs of realistic synthetic stars and galaxies
    with appropriate completeness for the Wide survey and reasonable five-band colors.

    For stars, we choose to use the sample from \citet{Leauthaud2007}.
    The authors select stars with clean photometry from the COSMOS images using not
    only the \texttt{SExtractor} stellar classification index (\texttt{CLASS\_STAR}),
    but also the peak surface brightness above background (\texttt{MU\_MAX}) and
    half-light radius (\texttt{RHL}).
    The classification is reliable down to $I_{\mathrm{F814W}}{\sim}25.2$ mag.
    We match this sample of stars with the HSC UltraDeep--COSMOS data that currently
    reaches to about ${\sim}27.2$ mag in $i$-band.
    After filtering the matched sample through basic quality cuts (see \ref{app:qc}),
    we gather 5-band HSC photometry for 14472 stars.
    To get a larger sample for the test, we resample the their 5-band magnitudes
    distributions using the \texttt{astroML} (\citealt{astroml}) alternative
    implementation of the \texttt{extreme-deconvolution} algorithm developed by
    \citet{Bovy2011}
    \footnote{\texttt{https://github.com/jobovy/extreme-deconvolution/}} to
    generate 100000 synthetic stars.
    In Fig \ref{fig:star_sample}, we show the magnitude and color distributions of
    the real COSMOS stars are nicely recovered by the resampled stars in all
    five-band magnitude and two color-color space.

    As for synthetic galaxies, we choose to use the single-\ser{} model of galaxies
    in the COSMOS field that have $I_{F814W} \leq 25.2$ mag.
    These models are created via method developed by \citet{Lackner2012} on the
    \textit{HST}/ACS images, and are included in \galsim{}.
    Each model is described by a total of 5 parameters: magnitude, effective radius,
    \ser{} index, axis ratio, and position angle.
    Although the single-\ser{} model is not always the best choice, its flexibility
    enables it to reasonably describe the flux distribution of most galaxies.
    Also its simplicity makes it easy to diagnose potential problems of the
    \cmodel{} photometry.
    We exclude a tiny fraction of ill-behaved models that have very high \ser{}
    index ($n_{\mathrm{Ser}} > 6.0$) or very low central surface brightness
    ($\mu_{i} < 24.0$\sb).
    We further match this COSMOS sample with the HSC UltraDeep--COSMOS data.
    after removing the objects with problematic photometry, we obtain the a sample of
    58210 synthetic galaxies with realistic 5-band HSC photometry.
    As shown in Fig \ref{fig:galaxy_sample}, the majority of these galaxies are
    faint ($i<24.0$ mag) and barely resolved ($R_{\mathrm{e}}< 1.0$\asec) galaxies.
    This sample is appropriate to test the general behaviours of photometry in
    \hscpipe{}, but is lack of relative bright galaxies ($i<20.5$ mag).

    We then create input catalogs via randomly distribute these synthetic stars and
    galaxies into the regions covered by the good and bad seeing \tracts{}.
    For stars (galaxies), we choose to use number density of 1000 (500)
    per CCD.

@@

%% ------------------------------------------------------------------------------------ %%
\subsection{Running \synpipe{} Test}
    \label{ssec:running}

    We conduct these tests on the cluster (\texttt{Master}) at Kavli-IPMU using
    the HSC DR1 data stored there.
    The \texttt{addFakes.py} step takes ${\sim}1.5$ hours per \tract{} in each
    band; same process takes longer for the test of galaxies (${\sim}3.0$ hours per
    \tract{} in each band) as the \galsim{} simulation is more time consuming.
    The \texttt{stack.py} and \texttt{multiBand.py} together take ${\sim}3.5$ hours
    per \tract{}.

    We match the results with the input catalogs using a 2 pixels matching radius
    to generate output catalogs for \forced{} and \unforced{} photometry
    in each band.
    We also match the input catalogs with the original HSC catalogs to identify the
    ``ambiguously blended'' objects that are right on top of the flux peak of a real
    object.
    These objects are useful in the WL-related statistical tests (see Murata et al.
    in prep. for more details), but will not help test photometry, hence they will
    be excluded later

    The detailed log of the entire tests can be found here:
    \url{goo.gl/VINOVP}.
    User should be able to reproduce the results presented in this work using this
    information.
    It can also serve as a brief manual for running \synpipe{} test.

@@

%% ------------------------------------------------------------------------------------ %%
\section{Results on Photometric Performance}
    \label{sec:result}

    Here we show the general performance of \hscpipe{} for stars (galaxies)
    mainly through the \forced{} PSF (\cmodel{}) photometry.
    Although \hscpipe{} provides more options (e.g. aperture and Kron photometry),
    these two are the most appropriate and relevant ones for magnitude and colors of
    star and galaxy as they consider the effects of PSF in different bands,
    and are consistent across all bands in terms of position and shape.

@@

    Now, we will look into the accuracies of PSF magnitudes in all five bands
    independently.
    In Fig \ref{fig:psf_mag}, we show the relations between the input magnitude and the
    magnitude difference from the \hscpipe{} \forced{} PSF photometry.

>>>>

    %% Challenges
    Before we can tackle any outstanding scientific questions, we must first learn
    how to handle the huge amount of data\footnote{Right now, SSP has accumulated 
    ${\sim}300$ TB of data products.} generated by these projects as well as achieve
    accurate photometric measurements of different types of objects.
    Data handling becomes increasingly challenging in the age of modern imaging
    surveys, in part due to variations and effects related to the cameras' 
    charge-coupled devices (CCDs).
    The cameras are often made up of multiple CCDs, each with slightly different 
    characteristics, and have large fields-of-view (FoV) over not perfectly flat 
    focus planes.
    During observation, the seeing and background conditions always show spatial
    and temporal variations across the FoV.
    The full-depletion, thick CCDs selected for the cameras enable long exposure 
    times and excellent sensitivity in the red-end, but they often suffer from the 
    so-called ``brighter-fatter'' effect (\citealt{Antilogus2014}), which means that 
    brighter stars appear larger than they are.
    These variations and effects make accurate astrometric and photometric calibration,
    background subtraction, and point spread function (PSF) modeling intrinsically
    difficult (e.g., \citealt{Schlafly2012}).
    The multi-epoch, multi-band nature of the surveys also complicate data reduction 
    because the scientist must pay special attention to image stacking, multi-band 
    object detection, and measurement processes.
    Furthermore, as ongoing surveys reach to increasingly deeper detection limit 
    (e.g., SSP Wide reaches to $5\ \sigma$ detection limit of point source of 
    ${\sim}26.4$ mag), the number of objects in a unit area, especially faint objects,
    becomes much higher. 
    In addition, it is much more common to observe objects that overlap each other at
    different levels (a phenomenon often referred to as ``blended'').
    These modern imaging survey challenges call for photometric measurement methods 
    that are more powerful and precise than those used in previous, shallower surveys.

@@

%% ------------------------------------------------------------------------------------ %%
%% Fig: Flowchart
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_flowchart_new}
    \end{center}
    \caption{
        Illustration of \synpipe{} basic procedures.
        Gray boxes indicate the required inputs at different stages.
        The blue box identifies the \texttt{addFakes.py} step, when \synpipe{} injects 
        simulated images of synthetic objects onto a single-frame image. 
        We show an example CCD image with and without synthetic objects on it
        (highlighted by green circles).
        Red boxes depict the subsequent image coadding and multiband measurement steps
        using \texttt{stack.py} and \texttt{multiBand.py} from \hscpipe{}.
        We show a small piece of \coadd{} image with synthetic objects on it.
        The figure on the right side of the middle row shows the spatial relation
        between \tract{} (outlined by the black dashed lines; each small region
        is a \texttt{Patch}) and all the \visits{} that contribute to it. 
        (Each \visit{} has a  unique color; each small region is the size of a CCD.)
        }
    \label{fig:flowchart}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    %% Basic
    Taking advantage of the new prime focus camera on the 8.2--m Subaru telescope,
    the ambitious HSC survey consists of three layers: Wide, Deep, and UltraDeep.
    The Wide layer will map a total of ${\sim}1400$ deg$^2$ of sky in five broad bands
    ($grizy$; Kawanomoto\etal in prep.).
    The Deep (four separated fields; ${\sim}27$ deg$^2$) and UltraDeep (two separated
    fields; ${\sim}3.5$ deg$^2$) layers will use a few additional narrow-band filters
    and employ a slightly different surveying strategy.
    Strauss\etal (in prep.) describes the HSC survey in more detail, and identifies the 
    HSC collaborators.

    The HSC camera (\citealt{Miyazaki2012}) is made up of 124 full-depletion thick 
    CCDs: 112 for science and another 12 for guiding and focusing.
    The camera has a circular FoV with a 1.5 deg diameter.
    Each CCD contains 2048$\times$4096 pixels distributed in four amplifiers.
    The pixel size is equal to 0.168\asec{} on the sky.

    In February 2017, the HSC collaboration released the first 1.7 years of data to 
    the public (DR1; 
    \citealt{HSCDR1})\footnote{\texttt{https://hsc-release.mtk.nao.ac.jp }}.
    For our work, we focused on data from the Wide layer as they relate to key 
    scientific goals of the HSC survey, which include WL cosmology, galaxy evolution 
    since $z{\sim}1$, and studies of galaxy clusters.
    The current Wide layer includes ${\sim}108$ deg$^2$ of sky isolated in
   six different regions (XMM--LSS, GAMA09H, WIDE12H, GAMA15H, HECTOMAP, and VVDS)
    \footnote{A small AEGIS field is also observed for calibration purposes.}.
    Except for the HECTOMAP field, the regions are all close to the equator. 
    In the Wide layer, the $g$ and $r$ bands have 10 mins of exposure broken into four
    dithers\footnote{Large, ${\sim}1/3$ of the FoV dither pattern is used to ensure
    uniform coverage.}; for the remaining three bands, 20 mins of exposure time and six
    dithers are used\footnote{Several 30 s exposures are taken to improve the 
    dynamic range.}.
    The survey prioritizes the observations so that the $i$-band can have excellent
    seeing conditions to help make accurate WL shape measurements.
    The current Wide layer has impressive median seeing with FWHM${\sim}0.6$\asec{},
    and has a $i{\sim} 26.4$ mag $5\sigma$ point source detection limit. 
    \citealt{HSCDR1} provides details on the first data release and data status.

@@

        \item \textbf{HSC Photometry}:
            The multi-band catalogs generated by \hscpipe{} contain a variety of 
            photometric information (see \citealt{HSCDR1} for details).
            \textbf{Here, we focus on the \forced{} \texttt{psf} and \cmodel{}
            photometry.}
            \texttt{psf} photometry should provide the most appropriate magnitudes and
            colors for point sources.
            Improved over the SDSS version (\citealt{Lupton2001, Abazajian2004}),
            the HSC \cmodel{} algorithm (described in Bosch\etal, in prep.) fits 
            each object's flux distribution using a combination of the de Vaucouleurs
            profile and an exponential component that takes the PSF convolution 
            into account.
            \cmodel{} is designed to yield accurate colors for galaxies.
            In addition, the star--galaxy classification task is performed based on 
            the difference between the \texttt{psf} and \cmodel{}{} magnitudes.

@@

        \item \textbf{Authentic Data Processing}:
            To follow the data reduction process as realistically as possible, we choose to
            start from the single-\visit{} images instead of directly putting synthetic 
            objects on the final \coadd{} images (e.g., \citealt{Suchyta2016}).
            Through this approach, subtle effects like seeing differences among
            \visits{} and small errors in astrometric calibration can be taken
            into account.
            Every synthetic object will experience all the steps we would use for any 
            real object: detection, deblending, stacking, and measurement.
            This can be important for challenging tasks like the WL measurements
            or the detection of high-$z$ galaxies.
            The only downside of this choice is that it will certainly slow down the
            test for \coadd{} images because in this approach we need to inject 
            synthetic objects into all the \visits{} that contribute to a \tract{}.

@@

        \item \textbf{Single- or Double-\ser{} model for galaxy}:
            \texttt{SynPipe} uses \galsim{} \texttt{v1.4} (\citealt{Rowe2015}) to
            simulate a galaxy.
            \galsim{} is an image simulation tool that has been well tested during
            the GRavitational lEnsing Accuracy Testing 3 (GREAT3) challenge 
            (\citealt{Mandelbaum2014}).
            Currently, \synpipe{} allows a synthetic galaxy to be modeled by single
            or double components that are described by the \citet{Sersic1963}
            profile\footnote{More flexible model choices will be added later.}.
            The \ser{} profile is flexible enough to describe the overall flux
            distributions of galaxies near and far, both early-type or late-type.
            A double-\ser{} model can simulate a galaxy with even more realistic
            structural details (e.g., bulge$+$disk).
            For each \ser{} component, the user needs to provide the magnitude,
            effective radius ($R_{\mathrm{e}}$; in unit of arcsec), \ser{} index
            ($n_{\mathrm{Ser}}$), axis ratio ($\mathrm{b}/\mathrm{a}$), and position
            angle (PA).
            External shear can also be applied to a synthetic galaxy ($g_1$ and 
            $g_2$; see \citealt{Rowe2015} for more details).

@@

    After \synpipe{} creates the image of the simulated galaxy, it then shifts the 
    image according to is location on the CCD on a pixel-by-pixel basis; 
    \synpipe{} also crops the images when necessary.
    When that task is complete, \synpipe{} adds appropriate noise to the image based 
    on the pixels it covers and the calibration information of the detector, and creates 
    a variance image that reflects the influence of the synthetic object.
    Since each HSC CCD consists of 4 amplifiers, each with different characteristics,
    \synpipe{} carefully creates a corresponding gain map to provide accurate noise 
    level.
    In the final step, \synpipe{} adds the noise-added image and the variance map to the
    original CCD data while also adding a new \texttt{FAKE} mask bit to the mask plane.
    The middle panel of Fig \ref{fig:flowchart} depicts the result of the
    \texttt{addFakes.py} step by showing an example CCD image before and after the
    synthetic objects are injected.
%% ------------------------------------------------------------------------------------ %%

@@

    As the last step, \synpipe{} matches the input catalog to the results within a
    radius that is specified by the user, and merges all the \unforced{} and
    \forced{} measurements from all the \texttt{Patches}.
    Each unmatched object from the input catalog is also passed to the results catalog 
    with a unique label.
    In the case of multiple matches, the user can choose between returning only the 
    closest match or returning all objects within the matching radius (the nearest one 
    is labeled as such).

    \song{Susan's edit ends here; and Song has went through the previous sections.}
    \susan{Susan made some minor additional edits to the preceding text on 4/17/2017.}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %%
%% Fig: Star Sample
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_star_sample}
    \end{center}
    \caption{
        Magnitude and color distributions of the synthetic stars.
        \textbf{Upper panel} shows the five-band magnitude distributions of the COSMOS
        stars (filled histograms) and the resampled stars (dashed lines).
        \textbf{Lower panel} shows their color-color distributions
        (left: $g-r$ v.s. $r-i$; right: $i-z$ v.s. $z-y$).
        We show the number density distribution of the COSMOS stars in hexagonal bins,
        and use contours for the resampled stars.
        }
    \label{fig:star_sample}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %%
%% Fig: Galaxy Sample
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_galaxy_sample}
    \end{center}
    \caption{
        Synthetic galaxy distributions of five-band magnitudes (\textbf{upper panel}) and other properties
        (\texttt{lower panel}; from left to right are the \ser{} index, axis ratio,
        effective radius in arcsec, the $g-r$ and $r-z$ colors).
        Objects used for the \textbf{Tract} with good seeing (filled histograms) and
        the one with bad seeing (dashed line) have almost identical distributions.
        }
    \label{fig:galaxy_sample}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %%
\susan{Susan started editing here on 4/17/2017.}
\section{Generation of Synthetic Dataset}
    \label{sec:test}

@@

    Given the \synpipe{} design and the HSC DR1 data volume \footnote{${\sim}70$
    TB of images}, it is not realistic to test the whole dataset. 
    For this work, we select two \tracts{} in HSC Wide regions
    that fit the following criteria:

@@

        \item Not distorted by an extremely bright ($i<12$ mag), saturated star.

        \item Can represent both good and bad seeing conditions in the current $i$-band
            data of the HSC survey.
              \end{enumerate}
              In addition to satisfying these criteria, the selected \tracts {}  show the photometric uncertainties under both good and bad seeing conditions, since for any given star or galaxy, different seeing conditions affect its
            central S/N on the \coadd{} images and, therefore, also impact the
            detection and deblending processes in \hscpipe{}.

The two selected HSC Wide regions are as follows:  
    \tract{}$=9699$ in the VVDS field (median FWHM$=0.449$\asec{} in $i$-band;
   in this paper referred to as \texttt{goodSeeing}) and
    \tract{}$=8764$ in the XMM-LSS field (median FWHM$=0.700$\asec{};
    \texttt{badSeeing}).
    \tract{}$=9699$ also has better seeing in both $r$- and $z$-bands;
    the seeing conditions in $g$- and $y$-bands are very similar for both  \tract{}$=9699$ and \tract{}$=8764$.
    For both \tracts{}, the \coadd{} image in each band includes data from
    20--40 \visits{}.

@@

    In this work, we use objects from the high-resolution \hst{}/ACS COSMOS field observations to build input catalogs of realistic synthetic stars and galaxies with appropriate completeness for the Wide survey and with reasonable five-band colors. We first select stars and galaxies as described below;  we then create the input catalogs via randomly distributing the selected synthetic stars and galaxies into the regions covered by the good- and bad-seeing \tracts{}. For stars, we use a number density of 1,000 per CCD; for galaxies, we use a number density of  500 per CCD.

For star selection, we use the sample from \citet{Leauthaud2007}. 
     We use not only the \texttt{SExtractor} stellar classification index (\texttt{CLASS\_STAR}) but also the peak surface brightness above background (\texttt{MU\_MAX}) and
    half-light radius (\texttt{RHL}) to select stars with clean photometry. 
    The classification is reliable down to $I_{\mathrm{F814W}}{\sim}25.2$ mag.
    We match this sample of stars with the HSC UltraDeep--COSMOS data that currently
    reach to about ${\sim}27.2$ mag in $i$-band.
    After filtering the matched sample through basic quality cuts (see \ref{app:qc}),
    we gather five-band HSC photometry for 14,472 stars.
    To get a larger sample for the test, we resample the five-band magnitude
    distributions using \texttt{astroML} (\citealt{astroml}) alternative
    implementation of the \texttt{extreme-deconvolution} algorithm developed by
    \citet{Bovy2011}
    \footnote{\texttt{https://github.com/jobovy/extreme-deconvolution/}} to
    generate 100,000 synthetic stars.
    In Fig \ref{fig:star_sample}, we show that the magnitude and color distributions of
    the real COSMOS stars are nicely recovered by the resampled stars in all
   five-band magnitude and two color-color space distributions. \susan{Later you use "2-D color-color" Should it also be 2-D here?}

For synthetic galaxies, we use the single-\ser{} galaxy models 
    in the COSMOS field that have $I_{F814W} \leq 25.2$ mag.
    These models are created via a method developed by \citet{Lackner2012} on the
    \textit{HST}/ACS images and are included in \galsim{}.
    Each model is described by a total of five parameters: magnitude, effective radius,
    \ser{} index, axis ratio, and position angle.
    Although the single-\ser{} model is not always the best choice, its flexibility
    enables it to reasonably describe the flux distribution of most galaxies.
    Also, its simplicity makes it easy for us to diagnose potential problems of the
    \cmodel{} photometry.
    We exclude a tiny fraction of ill-behaved models that have a very high \ser{}
    index ($n_{\mathrm{Ser}} > 6.0$) or a very low central surface brightness
    ($\mu_{i} < 24.0$\sb).
    We further match this COSMOS sample with the HSC UltraDeep--COSMOS data.
    After removing the objects with problematic photometry, we obtain a sample of
    58,210 synthetic galaxies with realistic five-band HSC photometry.
    As shown in Fig \ref{fig:galaxy_sample}, the majority of these galaxies are
    faint ($i<24.0$ mag) and barely resolved ($R_{\mathrm{e}}< 1.0$\asec).
    This sample is appropriate to test  \hscpipe{}'s general photometric behaviors, but the sample lacks relatively bright galaxies ($i<20.5$ mag).

@@

%% ------------------------------------------------------------------------------------ %%
\subsection{Running the \synpipe{} Tests}
    \label{ssec:running}

    We use HSC DR1 data stored at Kavli Institute for the Physics and Mathematics of the Universe (Kavli IPMU) to conduct the \synpipe{} tests on the cluster (\texttt{Master}).
    The \texttt{addFakes.py} step takes ${\sim}1.5$ hours per \tract{} in each
    band; the same process takes longer for the galaxy tests (${\sim}3.0$ hours per
    \tract{} in each band) because the \galsim{} simulation is more time consuming.
    The \texttt{stack.py} step and \texttt{multiBand.py} step together take ${\sim}3.5$ hours
    per \tract{}.

    We match the results with the input catalogs using a 2--pixel matching radius
    to generate output catalogs for \forced{} and \unforced{} photometry
    in each band.
    We also match the input catalogs with the original HSC catalogs to identify the
    ``ambiguously blended'' objects that are right on top of the flux peak of a real
    object. \susan{Is ambiguously blended well-understood by your reader? Or is the definition that they are objects that are right on top of the flux peak of a real object? If so, change sentence to the following: We also match the input catalogs with the original HSC catalogs to identify the  ``ambiguously blended'' objects, which are defined as those objects that are right on top of the flux peak of a real
    object.}
    The ambiguously blended objects are useful in the WL-related statistical tests (see Murata et al.
    in prep. for more details); but since they will not help test photometry, they will be excluded later.

    The detailed log of the entire tests can be found at 
    \url{goo.gl/VINOVP}.
    The user should be able to reproduce the results presented in this work using this information. It can also serve as a brief manual for running a \synpipe{} test.

@@

%% ------------------------------------------------------------------------------------ %%
\section{Photometric Performance Results}
    \label{sec:result}

    Here we discuss \hscpipe{}'s general performance, assessed mainly through  \forced{} PSF photometry (for stars) and (\cmodel{}) photometry (for galaxies).
 Although  \hscpipe{} does provide other options (e.g., aperture and Kron photometry), 
these two are the only options that consider the effects of PSF in different bands and are consistent across all bands in terms of position and shape. Therefore, they are the most appropriate and relevant to star and galaxy magnitudes and colors.

@@

    Now, we look into PSF magnitude accuracy in each of the five bands
    independently.
    Fig \ref{fig:psf_mag} shows the relation between the input magnitude and the
    magnitude difference from the \hscpipe{} \forced{} PSF photometry.
